Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-08 acl.2016/acl2016.tex
acl paper

This contrast with Moses which scales to approximately 16 threads but then actually become slower if more are used, Figure~\ref{fig:moses-speed}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{moses-scalability.png}} 
\end{tabular}
\caption{Moses decoding speed}
\label{fig:moses-speed}
\end{figure}

@@

>>>>

This contrast with Moses which scales to approximately 16 threads but then actually become slower if more threads are used, Figure~\ref{fig:moses-speed}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{moses-scalability.png}} 
\end{tabular}
\caption{Moses decoding speed}
\label{fig:moses-speed}
\end{figure}

@@

We verify the results we the smaller French-English phrase-based model and test set container longer sentences. The speed gain is even greater than our main testing scenario, Figure~\ref{fig:fr-en-speed}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{fr-en-speed.png}} 
\end{tabular}
\caption{Decoding speed for fr-en model}
\label{fig:fr-en-speed}
\end{figure}
